О множествах точек на плоскости с целочисленными расстояниями

### 2019-06-18 pps-linear-bound/pps-linear-lower-bound.tex
A small note
Replace the bold selection of 'open' with a remark on importance

\begin{lemma}
	\label{lem:intervals_cross}
	If \textbf{open} line segments $M_1 M_2$ and $M_3 M_4$ do not intersect,
	%$M_1 \neq M_2$, $M_3 \neq M_4$,
	then the set $cr(M_1,M_2) \cap cr(M_3,M_4)$ is either a straight line or contains 2 or 4 points.
\end{lemma}

@@

>>>>

\begin{lemma}
	\label{lem:intervals_cross}
	If open line segments $M_1 M_2$ and $M_3 M_4$ do not intersect,
	%$M_1 \neq M_2$, $M_3 \neq M_4$,
	then the set $cr(M_1,M_2) \cap cr(M_3,M_4)$ is either a straight line or contains 2 or 4 points.
\end{lemma}
It is important that we consider the intersection of open line segments,
so e.g. the cases $M_1 = M_3$ and $M_3 \in M_1 M_2$ satisfy the conditions of Lemma~\ref{lem:intervals_cross}.

@@

Therefore, we will focus on planar integral points sets of more than 21491 points.
